\section{Review}
The goal for this sprint was initially to set up Virtuoso and a C\# API end-point for Virtuoso in a development environment in Docker. 
Additionally, we also wanted to finish writing the report sections related to the first sprint of the \knox{} project. 
Due to changes in the goal specification during the sprint, our goals changed to setting up the WordCount database in Docker, as well as creating an API end-point for this, also contained in Docker.

\subsubsection*{What has been accomplished?}
As a result of the changes seen throughout the sprint, a large part of this sprint became a combination of research and replanning. 

We had planned to research and implement Virtuoso as per our supervisor's recommendation.
Unfortunately, the research and implementation was cut short because the priorities of the \knox{} project changed --- by request of the PO.

Most of the initial research into Virtuoso quickly became redundant, and as such, an effort had to be put into planning what actions to make based on the new requirements. 
Therefore, the only actually accomplishment in this sprint was finishing the aforementioned sections for the first sprint of the \knox{} project.  



\subsubsection*{What has changed in the environment?}
Rather large changes were seen in the environment during this sprint. As mentioned in section \ref{ssec:newRequirements} the initial goal set by the product owner of the \knox{} project had been vague in their definition. 
This meant that the goals that we had planned initially were irrelevant, as a better specified goal from \knox{} was presented over halfway through the sprint. 

\subsubsection*{What next?}
Based on the time constraint that we experienced due to the change in environment, all the work related to developing an API end-point for the WordCount database in C\# as well as containerizing both the API and the database had to be pushed into the third sprint.
