\section{Sprint Planning}
\subsection{Knox Goal}
The overall goal for the Knox project during this sprint was to get the search engine to work. To accomplish this goal the product owner specified a list of expectation that when completed would fufill a minimal viable product. The specified list is outlined in figure X.
\begin{itemize}
	\item It should be possible to make searches in all the available databases.
	\item It should be possible to make searches using keywords in all the available data.
	\item It should be possible to make searches in all Nordjyske articles from 2017-2021
	\item It should be possible to make searches in all the Grundfos manuals, barring those that have shown to be problematic during processing.
	\item The UI should minimaly be able to display a link to the given article but preferably dispaly the title and text.
\end{itemize}

With the overall goal for the sprint contained in figure x, a granulated sprint goal can be made, that takes into account the focus of our scrum group.

\textbf{Sprint goal}
As noted in the preceding sprint, the code base that was inherited from the previous iteration was deemed problematic and costly to maintain. Therefore our sprint goal for this iteration is based on updating the code base to better comply with the requirements for the Knox goal.

Based on this observation as well as the aforementioned requirements, our sprint goal is as follows:

\textit{Make the minimally required amount of API endpoints available to satisfy the requirements for the search engine and create the necessary documentation.}

\textbf{User Stories}
Under normal circumstances, this section would contain the user stories that were made for this iteration. Due to  


The sprint goal could then be granulated into subtasks needed to be completed in order to live up to the minimal viable product. With the tasks granulated a session of scrum poker was held in order to evulated their time requirements. Lastly the tasks was categorized by their priority and focuspoint and divided into three different sprint increments: Wordcount API, Write Report, Wiki Documentation. 






\subsection{Sprint goal}
%The sprint goal for this group
%How does our sprint goal help with the overall sprint goal
%The purpose and priority for each increment
%Show the available backlog
