\chapter{Introduction to Knox}\label{introduction_to_knox}
\textit{The following sections have been written in collaboration with other Knox project groups.}

Knox is a large-scale collaborative project offered at the 5th semester of the Software study program at Aalborg University in the fall of 2021. It is a multi-project in the sense that eight groups are to work together to facilitate a noticeable increment compared to the work of last year's 5th semester students, who initiated Knox. In other words - besides being a multi-group project, Knox is also a cross-semester project with each year's students handing over their contribution to future 5th semester students.\\

Knox is an acronym of The Knowledge Toolbox, and as the name implies it is a knowledge engineering toolbox. The vision for Knox is a flexible knowledge engineering toolbox with components that can be combined to solve bigger problems. Currently, the project is focused on processing documents with \textit{Nordjyske Mediehus} and \textit{Grundfos} as collaborators who supply large amounts of documents to hopefully be turned into knowledge through Knox.\\

With this semester, Knox is going into its second year of development, during which the role of product owner is carried out by a student from the previous year of Knox development. Project handover is done with the help of the product owner. The status of Knox at handover is that a foundation has been built by last year's students.
However, the search engine, Knox's most basic component, is not currently functional. Getting the search engine to a functional state is an important part of this year's development.\\

For the second year of development, there exist two primary stages.
The first stage is to get the pipeline with search engine functionality up and running as a minimum viable product (MVP). The MVP will be decided by the groups together with the product owner. The second stage is for the groups to individually extend their layer's functionality. This stage should hopefully bring the Knox pipeline beyond the MVP and give extended functionality to the toolbox.\\

To give a better idea of the Knox project as a whole, the pipeline will now be presented and explained. 

\input{sections/Chapter 1 - Introduction to knox/20_Knox-Pipeline.tex}
\input{sections/Chapter 1 - Introduction to knox/30_Communication.tex}
\input{sections/Chapter 1 - Introduction to knox/40_Agile-Cooperation.tex}
\input{sections/Chapter 1 - Introduction to knox/50_Committees.tex}

%*context for the project 
%		*purpose
%		*collaborators 
%*2nd year of knox and status of project at handover
%		*Handover and PO
%		*current status
%*Goal of second year (search engine)
%		*working search engine
%		*extension of individual layers
%*tail into next section (pipeline?)