\section{Redesigning the WordCount Database}
In section \ref{InitialDesign}, we established that the database design would lead to duplicate or redundant data in the WordCount database.
Namely, the terms occurring in the Term entity set (see section \ref{newdatabaseER}) will not be unique. 
Thus, the database can contain duplicate values.
 
To address this issue, we created relations using the relational model (see section \ref{relational_databases}) and ensured they are well-designed.
After ensuring that a normal form is reached, we created the relations using SQL as a DDL.
We also needed to adjust the data access models (see section \ref{models}) to ensure access using EF core.
When implementing the new database structures, we needed to ensure that the pipeline is operational and has minimum downtime. 
Therefore, we had to ensure we could always roll back changes to the code and database structures.
As described in section \ref{CI/CD}, we can easily deploy versions of our code.
By reverting the changes to the old implementation of the models, we were able to ensure a quick response in case the new implementation failed.
We needed to ensure that this was also the case for the database structures.
This was done by taking a dump (backup) of the database, and verifying that no database relations are deleted during the data migration.

\input{sections/Chapter 8 Sprint 6/CreatingNewModels.tex}
\input{sections/Chapter 8 Sprint 6/BCNF.tex}
\input{sections/Chapter 8 Sprint 6/ImplementingTheNewModels.tex}
\subsection{Result}
After having implemented the new database structure, we assessed the changes to the database. 
The number of words in the newly implemented \texttt{Word} relation is 260,000.
The number of unique tuples in the newly implemented \texttt{WordOccurance} table is 6,900,000, the same as the number of tuples representing words in the old \texttt{Term} relation.
Thus, the number of tuples in the new relation is the same, but the number of duplicate words have been reduced greatly.
