\section{Sprint Planning}
During this sprint, we focused on creating a functioning UI component, redesigning the database schemas to minimize the amount of stored data, as well as creating a video describing the flow of our endpoints. Furthermore, we wanted to deliver the knowledge graph components from the last sprint. 

\subsection*{User Stories}
This sprint focused on two user stories provided to us by the \knox{} PO, as well as one arranged by our own product owner. 
Due to the size of the user stories provided in this sprint, they were not seen as epics like they were in the last sprint. Thus, the user stories were not granulated and were instead added directly to the sprint backlog.  

\userStory{a future \knox{} member}{a video describing the flow of the WordCount database endpoint}{can gain an understanding of its workings}
\userStory{the database layer}{to redesign the database schemas}{can minimize the size of the data stored}
\userStory{the database layer}{to develop a simple UI component denoting the database status}{can see the database statuses on the \knox{} website}

A game of planning poker was then played in order to provide an estimation of the size of the tasks. 
Using this, we were able to decide which tasks we could bring over from the previous sprint.

\subsection*{Release Planning}
As we do not control the live branch for the deployed \knox{} website, the acceptance criteria for the UI component was creating a pull request with a functioning component and having that request accepted.
This procedure was established by the UI committee. 
For the WordCount database redesign, as well as the knowledge graph component started in the last sprint, the standard deployment procedure was expected. 