\section{Future works}
We suggest that next semesters' database group(s) restructure the WordCount database, making it BCNF. 
This can be done by creating tables for file paths and replacing the \texttt{filepath} attribute in the \texttt{article} table with a foreign key.
By doing this, one would reduce data redundancy for the WordCount database. 

We strongly suggest that the various databases of \knox{} migrate to a single, dedicated server.
This will greatly ease new implementations and management of both new and current of database structures.
Many of the layers will create, and need storage for, new data structures by analyzing currently stored data.
By centralizing the \knox{} databases, one could easily implement views or relationships connecting the data structures.

Future groups could also consider performance analysis for the methods of the API controllers. 
By doing this, they could ensure a stable response time for all endpoints.
Combining this with the UI component described in section \ref{UI}, the pipeline would have both a graphically representation of database status, as well as a more detailed description.
Monitoring of server resources would be beneficial in terms of streamlining the pipeline speed - however this has not been an issue so far.
One could use such resource analysis to create UI components and store analysis data in a database. 
It would also be beneficial to introduce \textit{logging \cite{ASPLogging}} to the various controllers, as to enable a persistent, yet customizable way, to describe errors, speeds, or feedback.
