\chapter{End-to-End Testing}\label{scrumofscrumendtotend}
\textit{The following sections have been written in collaboration with other Knox project groups.}
An end-to-end test was planned for the sprint to verify that the various implementations of the different layers fulfil the MVP when run in sequence. The test would entail scanning an article from Nordjyske and a manual from Grundfos in the preprocessing layer and delivering them in the correct format, as JSON, to the knowledge layer. The knowledge layer would then have to process the JSON, count the word frequencies in the document, and deliver this to the data layer. The data layer would then insert the given word frequencies, along with some metadata, into the database and make it accessible to the functionality layer, where the search engine itself could be used to search for word occurrences in the scanned documents.
By making sure that the documents could travel through the pipeline and be searched for through the search engine interface, we have shown that we fulfilled the MVP and therefore completed the goal for the third sprint.\\
The end-to-end test did not go as planned. The preprocessing layer of the pipeline had trouble communicating with the knowledge layer due to the delay in launching a communication API. Furthermore, the JSON schema for \textit{Nordjyske Mediehus} articles could not be verified by the knowledge layer.
The lower layers also had trouble communicating with each other, due to routing problems, however, this was fixed at the first end-to-end test. By the end of the test, the \textit{Grundfos} data did manage to enter the database. The search result would appear on the UI which could redirect the user to the associated PDF. In the beginning, the UI sent the wrong flags to search for in the database, which was fixed during the end-to-end test.\\
At the end of the end-to-end test, the MVP was not met. Because of this, an intermission between sprint three and sprint four was added. During this intermission a second end-to-end test took place the 3rd of November. This end-to-end test was completed successfully with the expected results and the MVP was met.