\chapter{Sprint 3}
We have chosen to combine our descriptions of the two previous sprints into one sprint. Sprint 2 was supposed to be the sprint where the search engine was fixed, but ended up being swallowed by planning and bureaucracy. For this reason, it also took sprint 3 to fully implement the search engine. Because of our choice to combine the two sprints, any reference to sprint 3 should be interpreted as referring to the combined sprint.

%Common / Overall goal for all Knox groups
\input{sections/Common writings/60_Introduction-to-search-engine.tex}
\input{sections/Chapter 5 Sprint 3/planning}\todo{sprint goal - as defined in collaboration with other groups and PO (Section \ref{})}
This chapter covers the development process during the third sprint. The third sprint covers the implementation of the needed database features for getting a functioning search engine. 


To accomplish this goal, the product owner specified a list of expectations for the entire \knox{} project that, when completed, would fulfill a minimal viable product. The specified list of common goals is outlined below.
\begin{itemize}
	\item It should be possible to make searches in all the available databases.
	\item It should be possible to make searches using keywords in all the available data.
	\item It should be possible to make searches in all Nordjyske articles from 2017-2021
	\item It should be possible to make searches in all the Grundfos manuals, barring those that have shown to be problematic during processing.
	\item The UI should at least be able to display a link to the given article but preferably also display the title and text.
\end{itemize}

With the overall goal for the sprint outlined, a granulated sprint goal could be made that accounts for the focus of our scrum group.

\input{sections/Chapter 5 Sprint 3/increment1}
\input{sections/Chapter 5 Sprint 3/Review.tex}
\input{sections/Chapter 5 Sprint 3/retrospective.tex}

